Theories of deliberated preference

### 2018-02-25 simple.tex
Rephr (minor)

It is also necessary to capture the evolution of the position of $i$ towards arguments over time: a repeated query using a given pair of arguments may yield different answers, for example because the repeated question has been interleaved with another query containing other arguments (which $i$ may still have in mind when answering the second repetition), or for any other known or unknown reason. The important information for us is the \emph{set} of answers that $i$ could give to a query involving two given arguments and a given topic, among the set $\{\prop, ¬\prop, \text{both}\}$.
Hence, given $\prop \in \alltopic$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \Set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind. The querying protocol is supposedly made so that for any $\prop \in \alltopic$, $\ileadsto^\prop = \ileadsto^{¬\prop}$.

@@

Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\powerset{\prop\text{-sure}, ¬\prop\text{-sure}, b)}$ (where $b$ means both possible). We The set designates all cumulated answers over time, thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason). We assume $b$ is observable as well.

>>>>

It is also necessary to capture the evolution of the position of $i$ towards arguments over time: a repeated query using a given pair of arguments may yield different answers, for example because the repeated question has been interleaved with another query containing other arguments (which $i$ may still have in mind when answering the second repetition), or for any other known or unknown reason. The important information for us is the \emph{set} of answers that $i$ could give to a query involving two given arguments and a given topic, among the set $\{\prop, ¬\prop, \text{both}\}$. The set designates all possible answers over time and over different order of asking the queries.
Hence, given $\prop \in \alltopic$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \Set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind. The querying protocol is supposedly made so that for any $\prop \in \alltopic$, $\ileadsto^\prop = \ileadsto^{¬\prop}$.

@@

Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\powerset{\prop\text{-sure}, ¬\prop\text{-sure}, b)}$ (where $b$ means both possible). We , thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason). We assume $b$ is observable as well.
